True versus apparent shapes of astrophysical bow shocks

### 2015-08-07 papers/Paper1/sec-application.tex
07/08/15 Output of the last few days

\begin{align}
N(r_{IF},\theta) = N_0 \cos^{0.5}\theta
\end{align}

This scenario can be described with the algebraic formalism of \citep{Canto:1996}.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

\begin{align}
N(r_{IF},\theta) = N_0 \cos^{0.5}\theta
\label{eq:nprop}
\end{align}

This scenario can be described with the formalism of \citep{Canto:1996}, who proposes an algebraic solution for the two winds interaction problem in the thin shell approximation. See figure.

\begin{figure}
\includegraphics[width=\linewidth]{2winds-scheme}
\caption{Schematic representation of the two winds problem. Any point in the shell is located with the coordinates
$(R,\theta)$, and $\theta_1$ is measured from the external wind position}
\label{fig:2-winds}
\end{figure}

 Combining equations (6),(9)-(11) and (19)-(23) from \citep{Canto:1996} and (\ref{eq:nprop}), we can solve numerically for $R(\theta)$, as shown in figure (add figure later). Also we can
obtain a relation between $\theta$ and $\theta_1$

\begin{align}
\theta_1\cot\theta_1 = 1+ 2\beta I(\theta)\cot\theta - \frac{4}{5}\beta\left(1-\cos^{5/2}\theta\right)
\label{eq:th1th}
\end{align}

\subsection{Characteristic Radii}

$R_0$ is obtained directly from equation () of \citep{Canto:1996} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.

Combinig equation (23) from \citep{Canto:1996} and  (\ref{eq:th1th}) evaluated at $\theta=\frac{\pi}{2}$, we can obtain $R_{90}$

\begin{align}
R_{90} \simeq \frac{\left(2.4\beta\right)^{1/2}}{1-0.8\beta}
\label{eq:r90}
\end{align}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:
